Spherical harmonic analysis of faceted spheroids identifies shaping strategies and standardisation at Qianshangying (North China)

### 2025-08-22 analysis/paper/paper.qmd
updates

plot(1:10, wss, type="b", pch=19, frame=FALSE,
     xlab="Number of clusters K",
     ylab="Total within-cluster sum of squares (WSS)",
     main="Elbow Method for Optimal K")

>>>>

elbow_test <-
  plot(1:10, wss, type="b", pch=19, frame=FALSE,
       xlab="Number of clusters K",
       ylab="Total within-cluster sum of squares (WSS)",
       main="Elbow Method for Optimal K")
